Making Sequential Programs Deterministic

### 2019-04-01 experiments.tex
formatting

The authors also reported the sources of flakiness
after manually inspecting these tests. We ran \TheDeterminismChecker on all these benchmarks with the objective
of measuring recall of our tool. We cloned all 21 repos and switched to the commit that had a flakiness issue as reported 
in~\cite{nondex}. Of these projects, \<handlebars> has a compile time failure which prevents us from running \TheDeterminismChecker on it. For benchmarks \<visualee>, \<easy-batch>, and \<vraptor>, we couldn't find
the sources of flakiness as reported in~\cite{nondex} anywhere in the respective repositories.
\TheDeterminismChecker reported the nondeterministic source locations correctly in the rest of the projects.
All these benchmarks and instructions to reproduce our results can be found at \href{https://github.com/t-rasmud/determinismCaseStudies}{https://github.com/t-rasmud/determinismCaseStudies}.
\todo{P4, P12 and P21 det checker isn't recognized?}

@@

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{4cm}|p{5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible \\
        P2 & Yes & YamlWriter.java: [224,28] & cast unsafe  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible \\ 
        P4 & * & Det checker not found  &   \\ 
        P5 & ** & Class.getDeclaredMethods not found &    \\ 
        P6 & Yes & OptionGroup.java: [55,40]  & argument type incompatible \\ 
        P6 & Yes & Option.java: [157,28]  &  assignment type incompatible\\
        P7(test error) & Yes* & checker/ tests/ determinism/P71.java: 5 & return type incompatible \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible   \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible   \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible  \\
        P8 & ** & getDeclaredFields not found &   \\
        P9 & Yes & Printers.java: [269,97]  &  enhancedfor type incompatible \\
        P10 & ** & getDeclaredFields not found  &  \\
        P11 & Yes & MapUtils.java: [20,50]   & enhancedfor type incompatible  \\
        P12 & Yes  & GSLayerEncoder21.java: [113,91]  & enhancedfor type incompatible \\
        P13 & ** & unbuildable handlebars &  \\
        P14 & Yes  & Maps.java: [91,69] & invalid element type   \\
        P15 & Yes & PkiMessageDecoder.java: [144,29]  &  enhancedfor type incompatible  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible  \\
        P17 & Yes & JSONObject.java: [674,51]  & assignment type incompatible  \\
        P18 & Yes & SubstitutableLoggerTest.java: [67,61]   & enhancedfor type incompatible  \\
        P19 & Yes & DataDictionaryEventSource.java: [73,78]  &  enhancedfor type incompatible  \\
        P20 & Yes & SaverImpl.java: [43,69]  &  return type incompatible  \\
        P21 & Yes & RestDocumentation.java: [419,50] &  argument type incompatible   \\ \hline
    \end{tabular}
\end{table}

>>>>

The authors also reported the sources of flakiness
after manually inspecting these tests. We ran \TheDeterminismChecker on all these benchmarks with the objective
of measuring recall of our tool. We cloned all 21 repos and switched to the commit that had a flakiness issue as reported 
in~\cite{nondex}. Of these projects, \<handlebars> has a compile time failure which prevents us from running \TheDeterminismChecker on it. For benchmarks \<visualee>, \<easy-batch>, and \<vraptor>, we couldn't find
the sources of flakiness as reported in~\cite{nondex} anywhere in the respective repositories.
\TheDeterminismChecker reported the nondeterministic source locations correctly in the rest of the projects.
All these benchmarks and instructions to reproduce our results can be found at \href{https://github.com/t-rasmud/determinismCaseStudies}{https://github.com/t-rasmud/determinismCaseStudies}.
\todo{P4 compile error: dependencies}

@@

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{4cm}|p{5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible \\
        P2 & Yes & YamlWriter.java: [224,28] & cast unsafe  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible \\ 
        P4 & * & compile dependency failure  &   \\ 
        P5 & ** & Class.getDeclaredMethods not found &    \\ 
        P6 & Yes & OptionGroup.java: [55,40]  & argument type incompatible \\ 
        P6 & Yes & Option.java: [157,28]  &  assignment type incompatible\\
        P7(test error) & Yes* & checker/ tests/ determinism/P71.java: 5 & return type incompatible \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible   \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible   \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible  \\
        P8 & ** & getDeclaredFields not found &   \\
        P9 & Yes & Printers.java: [269,97]  &  enhancedfor type incompatible \\
        P10 & ** & getDeclaredFields not found  &  \\
        P11 & Yes & MapUtils.java: [20,50]   & enhancedfor type incompatible  \\
        P12 & Yes  & GSLayerEncoder21.java: [113,91]  & enhancedfor type incompatible \\
        P13 & ** & unbuildable handlebars &  \\
        P14 & Yes  & Maps.java: [91,69] & invalid element type   \\
        P15 & Yes & PkiMessageDecoder.java: [144,29]  &  enhancedfor type incompatible  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible  \\
        P17 & Yes & JSONObject.java: [674,51]  & assignment type incompatible  \\
        P18 & Yes & SubstitutableLoggerTest.java: [67,61]   & enhancedfor type incompatible  \\
        P19 & Yes & DataDictionaryEventSource.java: [73,78]  &  enhancedfor type incompatible  \\
        P20 & Yes & SaverImpl.java: [43,69]  &  return type incompatible  \\
        P21 & Yes & RestDocumentation.java: [419,50] &  argument type incompatible   \\ \hline
    \end{tabular}
\end{table}
